Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-09 paper/main.tex
Removed redundant paragraph.

\subsection{Face Recognition Stage Benchmarks}
\label{sec:recognition_benchmark}
Since we use a reduced training set for the recognition stage, our third
experiment was to find the relationship between the probability that the true
subject is in the training set vs the number of users in the reduced training
set and the speed of the recognition stage w.r.t.  the number of subjects in
the training set.

\subsection{Face Recognition Benchmark}
\label{sec:pipeline_benchmark}
The fourth experiment compares the recognition rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.

>>>>

\subsection{Face Recognition Stage Benchmarks}
\label{sec:recognition_benchmark}

\subsection{Face Recognition Pipeline Benchmarks}
\label{sec:pipeline_benchmark}
The fourth experiment compares the recognition rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.
